---
title: "Responding to Gentrication?"
author: 
  - Danielle Corcoran ^[American University]
  - Jeremy Joy ^[American University]
date: "2022-12-14"
abstract: "This is our informative abstract of fewer than 200 words. It describes what we investigate, how we investigate it, and what we find."
output: 
  pdf_document:
    number_sections: true
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE}
# This chunk might read our data.
# It might clean the data, create new variables, etc.
# Now our data are ready for our paper.
# Because echo=FALSE, this chunk itself is not shown.
# Because message=FALSE, any R messages from this chunk do not appear in our paper.
data("cars")
```

```{r eval=FALSE, echo=FALSE}
# Because eval=FALSE, this chunk is not run.
df <- read.csv()
```

# Introduction

In this section, we introduce the reader to the phenomenon we investigate. We describe the way in which our analysis contributes to an important intellectual debate, or how it answers a pressing political or social question. We introduce our hypotheses, data, and results. We signpost for the reader what's coming in the rest of the paper.

# Background

Here we go deeper into the intellectual debate, the political and social context of our investigation. To give the reader a clear sense of why we are writing this paper, we describe the relevant scholarly, technical, or popular literature. We cite at least two published, peer-reviewed scholarly works. For example, we could cite @bhavsar2020 like this or like this [@bhavsar2020]. @bhavsar2020 provides a systematic review of defining gentrification for epidemiologic research. We only cite others' work in our paper when it enhances the reader's understanding of what we, the authors of this paper, are doing. We connect everything we cite to *our* investigation; this is our original research, not a book report or an annotated bibliography.

In order to integrate citations into the References section below, we use the @ symbol (see bhavsar2020 above). This seems to work best in visual mode because it will pull up a drop down list of reference names from zotero (which must be open on your computer). Once you select the reference you want from the drop down menu it will ask you if you want to add it to the `reference.bib`. Then from there RMarkDown will auto populate all the references you cite while writing. We store `reference.bib` in the same folder as our paper's `.Rmd` and `.pdf` files. Its entries are formatted so that they can be knit to `.pdf`; see [https://j.mp/2UzTXEZ](https://www.overleaf.com/learn/latex/Bibliography_management_with_bibtex#The_bibliography_file) for example entries for articles, books, and miscellaneous. Zotero will generate these entries as long as the reference is in our group library or we can get these entries automatically from Google Scholar by turning on BibTeX in the Google Scholar Settings - Bibliography Manager.

# Data

\label{section:data}

This section describes the data we analyze. We describe the source of the data, and its primary features. We describe the methods we use to answer our question and to test our hypotheses.

If our data were `cars`, loaded in the chunk above, we could note that our data have `r nrow(cars)` observations.

# Methods and Results

Here, we explain and interpret our results. We try to learn as much as we can about our question as possible, given the data and analysis. We present our results clearly. We interpret them for the reader with precision and circumspection. We avoid making claims that are not substantiated by our data.

Note that this section may be integrated into Section \ref{section:data}, if joining the two improves the overall presentation.

Our results for the `cars` data include estimating the linear model

$$\text{Distance}_i = \beta_0 + \beta_1 (\text{Speed}_i) + \epsilon_i.$$

```{r echo=FALSE}
# Estimate a linear model:
lm_out <- lm(dist ~ speed, data = cars)
# Extract the coefficient on speed:
cars_speed_coef <- coef(lm_out)["speed"]
```

Below we show the model estimates. The first table uses `xtable()`, the second uses `stargazer()`.

```{r echo=FALSE, message=FALSE, results='asis'}
# We can print regression tables with xtable or stargazer:
regr_table <- xtable::xtable(lm_out,
                             digits = 2,
                             caption = "Our Informative Caption")
print(regr_table, comment = FALSE)
```

```{r echo=FALSE, message=FALSE, results='asis'}
# We can print regression tables with xtable or stargazer:
stargazer::stargazer(lm_out, 
                     title = "Our Informative Title",
                     dep.var.caption = "Outcome",
                     digits = 2,
                     header = FALSE)
```

Using the `cars` data, we find that each unit of speed is associated with `r round(cars_speed_coef, 1)` more units of distance.

# Discussion

We remind the reader what this paper was about, why it was important, and what we found. We reflect on limitations of the data or methods. If we have specific advice for someone picking up where we leave off, we provide that guidance. We avoid making trite statements like "more research should be done".

\newpage

# References
